学術論文

### 2023-03-29 articles-japanese.Rmd
update

- [45] 宮崎友里・重松潤・大井瞳・笹森千佳歩・山田美紗子・高階光梨・国里愛彦・井上真里・竹林由武・宋龍平・中島俊・堀越勝・久我弘典(印刷中). 心理療法におけるインフォームド・コンセント(Informed Consent: IC)の役割と最近の動向：ナラティブレビュー 認知行動療法研究

>>>>

- [45] 宮崎友里・重松潤・大井瞳・笹森千佳歩・山田美紗子・高階光梨・国里愛彦・井上真里・竹林由武・宋龍平・中島俊・堀越勝・久我弘典(2022). 心理療法におけるインフォームド・コンセント(Informed Consent: IC)の役割と最近の動向：ナラティブレビュー 認知行動療法研究, 48(3), 247-259.

### 2023-03-29 articles.Rmd
業績のメモ追加
update

- [43] Buchanan, E. M., ... Kunisato, Y., ... Primbs, M. (in press).
The Psychological Science Accelerator's COVID-19 rapid-response dataset.
Scientific Data.

- [42] Kowal, M.,... Kunisato, Y., ...Zumárraga-Espinosa, M.(in press) Predictors of Enhancing Human Physical Attractiveness: Data from 93 Countries. Evolution and Human Behavior.[Link](https://www.sciencedirect.com/science/article/pii/S1090513822000472)

@@

- [41] Dorison, C.A., Lerner, J.S., Heller, B.H... Kunisato, Y.,... Nicholas A. Coles (2022). In COVID-19 Health Messaging, Loss Framing Increases Anxiety with Little-to-No Concomitant Benefits: Experimental Evidence from 84 Countries. Affective Science. [link](https://doi.org/10.1007/s42761-022-00128-3)

@@

- [38] Somatori, K. & Kunisato, Y. (2022) Metacognitive Ability and the Precision of Confidence. Frontiers in Human Neuroscience, section Cognitive Neuroscience [Link](https://www.frontiersin.org/articles/10.3389/fnhum.2022.706538/abstract)

@@

- [33] Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(2021) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students. Current Psychology. [Link](https://doi.org/10.1007/s12144-020-01287-x)

- [32] van Doorn, J., van den Bergh, D., Dablander, F., van Dongen, N., Derks, K., Evans, N., Gronau, Q., Haaf, J., Kunisato, Y., Ly, A., Marsman, M., Sarafoglou, A., Stefan, A., & Wagenmakers, EJ.(2011) Strong public claims may not reflect researchers' private convictions. Significance, 18(1), 44-45.[Pre Print](https://psyarxiv.com/pc4ad/)

>>>>

- [44] Hamatani, S., Matsumoto, K., Kunisato, Y., Okawa, S., Yamashita, M., Mizuno, Y. (in press) Dismantling cognitive-behavioral therapy components for attention-deficit hyperactivity disorder in adolescents and adults: protocol for a network meta-analysis. BMJ Open

- [43] Buchanan, E. M., ... Kunisato, Y., ... Primbs, M. (2023). The Psychological Science Accelerator’s COVID-19 rapid-response dataset. Scientific Data, 10, 87.

@@

- [42] Kowal, M.,... Kunisato, Y., ...Zumárraga-Espinosa, M.(2022) Predictors of Enhancing Human Physical Attractiveness: Data from 93 Countries. Evolution and Human Behavior, 43(6), 455-474. [Link](https://www.sciencedirect.com/science/article/pii/S1090513822000472)

- [41] Dorison, C.A., Lerner, J.S., Heller, B.H... Kunisato, Y.,... Nicholas A. Coles (2022). In COVID-19 Health Messaging, Loss Framing Increases Anxiety with Little-to-No Concomitant Benefits: Experimental Evidence from 84 Countries. Affective Science, 3(3), 577-602.  [link](https://doi.org/10.1007/s42761-022-00128-3)

@@

- [38] Somatori, K. & Kunisato, Y. (2022) Metacognitive Ability and the Precision of Confidence. Frontiers in Human Neuroscience, section Cognitive Neuroscience，16, 10.3389/fnhum.2022.706538 [Link](https://www.frontiersin.org/articles/10.3389/fnhum.2022.706538/abstract)

@@

- [33] Shimono, Y., Hasegawa, A., Tsuchihara, K., Tanaka, K., Matsuda, Y., & Kunisato, Y.(2021) Longitudinal association between autistic traits and affinity for hikikomori in Japanese university students. Current Psychology, 41, 8842–8849. [Link](https://doi.org/10.1007/s12144-020-01287-x)

- [32] van Doorn, J., van den Bergh, D., Dablander, F., van Dongen, N., Derks, K., Evans, N., Gronau, Q., Haaf, J., Kunisato, Y., Ly, A., Marsman, M., Sarafoglou, A., Stefan, A., & Wagenmakers, EJ.(2021) Strong public claims may not reflect researchers' private convictions. Significance, 18(1), 44-45.[Pre Print](https://psyarxiv.com/pc4ad/)
